---
title: "CATS_basker_analysis"
output: html_document
---

Here I'm going to bring in the initial raw dataset from CATSCam, shark 2
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/Desktop/Basking sharks/bs.git")
ID <- 2 #this allows us to change the ID to look at other data if we want to 
data <- read.csv(paste0("Shark ", ID, "_CATS.csv"))
head(data)
table(data$Date) #so, all have the same date (July 26, 2013)
data$Time[1] #first time: 19:16:45
data$Time[nrow(data)] #end time: 22:10:47
```
So, now we need to think about what we are interested in. We want to know time, feeding, pressure, temperature, light intensity, ODBA

```{r}
dat2 <- data[,c(2,4, 5, 12, 19, 20, 21, 22)]
head(dat2)
#convert time to POSIXct
dat2[,1] <- as.POSIXct(dat2$Time, format="%H:%M:%OS", tz="UTC")
head(dat2)
colnames(dat2) <- c("Time", "Feeding", "Pressure", "Temp1", "Temp2", "Light", "Temp.ext", "ODBA") #still don't know what some of these things are - need to ask Heather
```


Let's look at frequency distribution of feeding events:
```{r}
feed.dat <- dat2[dat2$Feeding==1,]
summary(feed.dat)
# need to bin by duration of feeding event, which requires defining feeding events
feed.dat$Time
length(feed.dat$Time)
# should define feeding events by any difference in time > 00:10
interv <- feed.dat$Time[-1]-feed.dat$Time[-length(feed.dat$Time)]
table(interv)
splits <- which(interv > 10) #this gives us the locations of where the difference is greater than 10
length(splits)
head(feed.dat)

#### practice with one segment of feeding behavior: 

feed.dat1 <- (feed.dat[0:splits[1],])
ft1 <- feed.dat1[nrow(feed.dat1),1] - feed.dat1[1,1] #returns a difftime object and time difference that gives you the duration of the feeding event
ft1 <- as.numeric(feed.dat1[nrow(feed.dat1),1] - feed.dat1[1,1]) #make numeric

### now try with two segments, and combine in a list
feed.dat2 <- (feed.dat[splits[1]:splits[2],])
ft2 <- as.numeric(feed.dat2[nrow(feed.dat2),1] - feed.dat2[1,1]) 

#create a vector with the ft values
vec <- c(ft1, ft2)






######################################################

feed.dat3 <- (feed.dat[splits[2]:splits[3],])
feed.dat4 <- (feed.dat[splits[3]:splits[4],])
feed.dat5 <- (feed.dat[splits[4]:splits[5],])
feed.dat6 <- (feed.dat[splits[5]:splits[6],])
feed.dat7 <- (feed.dat[splits[6]:splits[7],])
feed.dat8 <- (feed.dat[splits[7]:splits[8],])
feed.dat9 <- (feed.dat[splits[8]:splits[9],])


trashlist<- list(feed.dat1, feed.dat2)
## now just trying to set this up in a list:
for (i in 1:1){
  trashlist[i] <- assign(paste("feed.dat",i), data=feed.dat) 
}


temp <- NULL
listofdfs <- list()

for(i in 1:59){
  listofdfs[[i]] <- data.frame(feed.dat
                               
                               [splits[i]:splits[i+1],])
# save your dataframes into the list
}
  


```

We then need to filter out the data from the surface, because the wobble affects the accelerometer 


Then, we are just going to do basic GLMs, testing ODBA if it were applied for the entire period versus if it's just the times that they're selecting